Behavior Driven Development in Haskell

### 2012-05-30 paper.tex
better introduction of Solution.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Problem}

@@

\begin{quote}
    \emph{kazu: We should explicitly repeat that we propose to Doctest as a BDD tool here..}
\end{quote}

To be able to specify evidence for users, we propose to add new
markup to Haddock and to use Doctest integrated with QuickCheck. To
describe evidence for developers, we propose to use Hspec also
integrated with QuickCheck.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Problem}
\label{sec:problem}

@@

As we explained in Section \ref{sec:problem},
we use Doctest for user documentation and Hspec for code documentation.
The following subsections explain two new markups of Haddock
and evidence combinators for Hspec.
